---
title: "WUP_08"
author: "Jamal Evans"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Introduction
$H_0$ is that there is no difference in neck lengt rate based on sex.

$H_A$ is that there IS a difference in death rate

##Methods



## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
This linear model shows that length~neck is a positive progressing line model.

#Numerical Results
```{r}
cor(NECK~LENGTH,data=bears)
```
Numerical results error in posit code...?
#Inferential Results(fisherpvalue)
```{r}
model.1 <- lm(NECK~LENGTH,data=bears)
summary.lm(model.1)
```
Our T value results to 0.00572 meaning that we reject the null hypothesis.

##Conclusion

Since the p-value associated with the coefficient for LENGTH is reported as "< 2.2e-16", which is essentially zero, we have very strong evidence to reject the null hypothesis. This indicates that there is a statistically significant relationship between LENGTH and NECK, as the coefficient for LENGTH is significantly different from zero. Based on the provided output, we would reject the null hypothesis.


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

